\Title

### 2021-02-18 manuscript/content.tex
Restore text from one of the items

\begin{enumerate}
  \item Define a set of $M$ equivalent sources distributed throughout the
    survey area.
  \item Define a set of $K$ overlapping windows of equal size that cover the
    survey area.
  \item Create $K$ separate sets of equivalent sources, one for each window.
    Each set will be formed by the portion of the original $M$ sources that
    fall inside the respective window.
    Since the windows overlap, the total number of sources from all sets will
    be greater than $M$.
  \item Define the vector $\mathbf{c}_k$ as the coefficients of the equivalent
    sources of the $k$-th window and matrix $\mathbf{A}_k$ as the Jacobian
    matrix between those sources and every data point of the survey.
  \item Model the predicted data as a superposition of the effects of the $K$
    separate sets of equivalent sources.
\end{enumerate}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{figs/gradient-boosting-schematics.pdf}
    \caption{
        Sketch of the gradient-boosted equivalent source algorithm.
        Given a set of data points (blue upwards triangles), define a set of
        equivalent sources (orange dots) by locating one source below each
        observation point.
        Start the gradient-boosting algorithm by selecting the data points and
        the sources that fall under one of the overlapping windows, and
        estimate their coefficients by fitting against this portion of the
        data.
        Then predict the effect of this set of sources on every observation
        point and calculate the residuals (red downward triangles).
        Use another window to select residual points and sources that fall
        under it, and estimate their coefficients by fitting them against the
        selected residual points.
        Predict the effect of this set of sources on every observation point
        and update the residuals.
        Repeat this step for every remaining window.
        The order in which the windows are covered is randomized to improve
        convergence of the algorithm.
    }
    \label{fig:gradient-boosting-schematics}
\end{figure*}

>>>>

\begin{enumerate}
  \item Define a set of $M$ equivalent sources distributed throughout the
    survey area (see section \ref{sec:source_distribution} for details).
  \item Define a set of $K$ overlapping windows of equal size that cover the
    survey area.
  \item Create $K$ separate sets of equivalent sources, one for each window.
    Each set will be formed by the portion of the original $M$ sources that
    fall inside the respective window.
    Since the windows overlap, the total number of sources from all sets will
    be greater than $M$.
  \item Define the vector $\mathbf{c}_k$ as the coefficients of the equivalent
    sources of the $k$-th window and matrix $\mathbf{A}_k$ as the Jacobian
    matrix between those sources and every data point of the survey.
  \item Model the predicted data as a superposition of the effects of the $K$
    separate sets of equivalent sources.
\end{enumerate}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{figs/gradient-boosting-schematics.pdf}
    \caption{
        Sketch of the gradient-boosted equivalent source algorithm.        
        Data points are represented by blue upwards-facing triangles,
        equivalent sources by orange dots, data residuals by red downwards-facing 
        triangles, and the current window by black dashed lines.
        The algorithm starts by selecting the data and sources 
        inside the first window and estimating the source coefficients 
        using the selected data points.
        Then, the effect of the estimated sources is predicted on all data
        points and used to calculate the residuals.
        Another window is used to select residuals and sources and 
        estimate the coefficients using the selected residuals instead of the 
        original data.
        Again, the effect of the estimated sources is predicted on all data points
        and the residuals are updated.
        These steps are repeated for every window in a randomized order.
    }
    \label{fig:gradient-boosting-schematics}
\end{figure*}
